Sound and Automated Synthesis of Digital\\ Stabilizing Controllers for Continuous Plants \thanks{Supported by EPSRC grant EP/J012564/1, ERC project 280053 (CPROVER) and the H2020 FET OPEN SC$^2$.}

### 2017-03-03 hscc2017/paper.tex
nudge

\renewcommand{\baselinestretch}{0.99}
\allowdisplaybreaks
\include{macros}

@@

By combining and applying state-of-the-art synthesis engines we present a
tool that automatically generates digital controllers for a given continuous
plant model that are correct by construction.  This approach delivers a high
degree of automation, promises to reduce the cost and time of development of
digital control dramatically, and requires considerably less expertise than
a-posteriori verification.  Specifically, we synthesize stable,
software-implemented embedded controllers along with a model of a physical
plant.  Due to the complexity of such closed-loop systems, in this work we
focus on linear models with known configurations, and perform parametric
synthesis of stabilizing digital controllers (further closed-loop performance
requirements are left to future work).

@@

\item We automatically generate {\em correct-by-construction} digital
  controllers using an inductive synthesis approach.  Our application of program
  synthesis is non-trivial and addresses challenges specific to control
  systems, such as the effects of quantizers and FWL.  In particular, we
  have found that a two-stage verification engine that continuously refines
  the precision of the fixed-point representation of the plant yields a
  speed-up of two orders of magnitude over a conventional one-stage
  verification engine.

@@

\bibliographystyle{abbrv}
\bibliography{paper}

>>>>

\renewcommand{\baselinestretch}{0.991}
\allowdisplaybreaks
\include{macros}

@@

By combining state-of-the-art synthesis engines we present a tool that
automatically generates digital controllers for a given continuous plant
model that are correct by construction.  This approach delivers a high
degree of automation, promises to reduce the cost and time of development of
digital control dramatically, and requires considerably less expertise than
a-posteriori verification.  Specifically, we synthesize stable,
software-implemented embedded controllers along with a model of a physical
plant.  Due to the complexity of such closed-loop systems, in this work we
focus on linear models with known configurations, and perform parametric
synthesis of stabilizing digital controllers (further closed-loop
performance requirements are left to future work).

@@

\item We automatically generate {\em correct-by-construction} digital
  controllers using an inductive synthesis approach.  Our application of program
  synthesis is non-trivial and addresses challenges specific to control
  systems, such as quantizers and FWL.  In particular, we
  have found that a two-stage verification engine that continuously refines
  the precision of the fixed-point representation of the plant yields a
  speed-up of two orders of magnitude over a conventional one-stage
  verification engine.

@@

\newpage
\bibliographystyle{abbrv}
\bibliography{paper}
